Paper 3 - Causal Roadmap

### 2023-05-26 docs/causal_roadmap.qmd
Fixed issues with authors names in PDF and acronyms.

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - ../../../all_phd/scholarly-metadata.lua
  - ../../../all_phd/author-info-blocks.lua
  - acronyms
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

>>>>

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - acronyms
  - authors-block
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---
